\theseminartitle \\ \small \thetitle

### 2021-09-09 tex/paper.tex
Added base paper structure

%*********************************************************************%
% META                                                                %
%*********************************************************************%
\ifgerman{
	\newcommand{\university}{Universität des Saarlandes}
	\newcommand{\school}{Saarland Informatics Campus}
}{
\newcommand{\university}{Saarland University}
\newcommand{\school}{Saarland Informatics Campus}
}
\ifgerman{ 
	\newcommand{\thetitle}{Seminar: Title of the Seminar}
	\newcommand{\shorttitle}{Seminar: Title of the Semianr}
	\newcommand{\thedate}{18. Oktober}
}{
\newcommand{\thetitle}{Seminar: Systems Benchmarking}
\newcommand{\shorttitle}{Seminar: Systems Benchmarking}
\newcommand{\thedate}{April 15}
\newcommand{\thegermandate}{15. April}
}

@@

% Advisors
\ifgerman{
	\newcommand{\advisor}{Betreuer}
	}{
	\newcommand{\advisor}{Advisors}
	}
	\newcommand{\advisors}{Prof. Sven Apel, \\ Christian Hechtl}

% Title for the seminar
\ifgerman{
	\newcommand{\theseminartitle}{Titel des Arbeit}
}{
	\newcommand{\theseminartitle}{"Performance Measurements Before Releases vs. Each Commits" -- Experiment Idea}
}

@@

	% Introduction
	\ifgerman{\section{Einführung}}{\section{General}}
	This document will briefly outline the experiment idea for the topic "Performance Measurements Before Releases vs. Each Commits" in the seminar "Systems Benchmarking". The goal of this experiment and the corresponding paper is to showcase, how continous performance measurements throughout the whole development process can be used to detect and fix performance regressions at a very early stage.

>>>>

%*********************************************************************%
% META                                                                %
%*********************************************************************%
\newcommand{\university}{Saarland University}
\newcommand{\school}{Saarland Informatics Campus}
\newcommand{\thetitle}{Seminar: Systems Benchmarking}
\newcommand{\shorttitle}{Seminar: Systems Benchmarking}
\newcommand{\thedate}{April 15}
\newcommand{\thegermandate}{15. April}

@@

% Advisors
	\newcommand{\advisor}{Advisors}
	\newcommand{\advisors}{Prof. Sven Apel, \\ Christian Hechtl}

% Title for the seminar
	%\newcommand{\theseminartitle}{"Performance Measurements Before Releases vs. Each Commits"}
	\newcommand{\theseminartitle}{"Using Continuous Benchmarking in Productive Systems -- Opportunities and Challenges"}

@@

% General Structure
	% 1. Introduction and Motivation
	% 2. General Definitions
	%		2.1 What is a Benchmark
	%		2.2 What is a continuous Benchmark
	% 3. Experiment
	%		3.1 Experiment Idea&Goals
	%		3.2 Setup
	%		3.3 Evaluation
	%	4.

	% Introduction
	\section{General}
	This document will briefly outline the experiment idea for the topic "Performance Measurements Before Releases vs. Each Commits" in the seminar "Systems Benchmarking". The goal of this experiment and the corresponding paper is to showcase, how continous performance measurements throughout the whole development process can be used to detect and fix performance regressions at a very early stage.
